Quantifying the home ground advantage

### 2022-04-21 inst/home_advantage.Rmd
typos

```{r,label=testhomegroundadvantageAgresti,cache=TRUE}
samep.test(H,teams)
```

@@

```{r,label=makeAgrestimatrix}
baseball_table <- matrix(c(
NA,   4+3i, 4+2i, 4+3i, 6+1i, 4+2i, 6+0i,
3+3i, NA  , 4+2i, 4+3i, 6+0i, 6+1i, 4+3i,
2+5i, 4+3i, NA  , 2+4i, 4+3i, 4+2i, 6+0i,
3+3i, 5+1i, 2+5i, NA  , 4+3i, 4+2i, 6+1i,
5+1i, 2+5i, 3+3i, 4+2i, NA  , 5+2i, 6+0i,
2+5i, 3+3i, 3+4i, 4+3i, 4+2i, NA  , 2+4i,
2+5i, 1+5i, 1+6i, 2+4i, 1+6i, 3+4i, NA),7,7)
teams <- c("Miulwaukee", "Detroit", "Toronto", "New York", "Boston","Cleveland","Baltimore")
rownames(baseball_table) <- teams
colnames(baseball_table) <- teams
M <- baseball_table # saves typing
```

@@

>>>>

```{r,label=homegroundAgresti,cache=TRUE}
samep.test(H,teams)
```

@@

```{r,label=makeAgrestimatrix}
baseball_table <- matrix(c(
NA,   4+3i, 4+2i, 4+3i, 6+1i, 4+2i, 6+0i,
3+3i, NA  , 4+2i, 4+3i, 6+0i, 6+1i, 4+3i,
2+5i, 4+3i, NA  , 2+4i, 4+3i, 4+2i, 6+0i,
3+3i, 5+1i, 2+5i, NA  , 4+3i, 4+2i, 6+1i,
5+1i, 2+5i, 3+3i, 4+2i, NA  , 5+2i, 6+0i,
2+5i, 3+3i, 3+4i, 4+3i, 4+2i, NA  , 2+4i,
2+5i, 1+5i, 1+6i, 2+4i, 1+6i, 3+4i, NA),7,7)
teams <- c("Milwaukee", "Detroit", "Toronto", "New York", "Boston","Cleveland","Baltimore")
rownames(baseball_table) <- teams
colnames(baseball_table) <- teams
M <- baseball_table # saves typing
```

@@

As an interesting aside, suppose we have some additional data from
games in which (for some reason), the home advantage was not
operating.

```{r,label=newinfotobaseball}
M2 <- matrix(c(0,1,2,0),2,2)
dimnames(M2) <- list(winner=teams[1:2],loser=teams[1:2])
M2
```

Thus we have additional data from three games in which Milwaukee won
twice and lost once.  This additional information may easily be
incorporated into our likelihood function, at least on the assumption
of independence:

```{r,label=addsomenewinfotobaseball}
baseball <- baseball + pairwise(M2)
```

We may assess the difference that the new information makes:

```{r,label=baseballtransplot,cache=TRUE}
ordertransplot(baseball_maxp[1:7],maxp(baseball)[1:7],xlab="old",ylab="new",plotlims=c(0.1,0.16))
```

Above, we see very little difference in the two evaluates, except for
Detroit and Milwaukee, as expected.
